\documentclass{shivank_cv}
\DeclareUnicodeCharacter{00A0}{ }

\begin{document}

\makecvtitle

\section{Education}

\cventry{CGPA:\textit{8.34/10}(Upto 2nd sem.)}{IIIT Bhubaneswar}{Bachelor of Technology,Information Technology}{2016--present}{}{}

\cventry{Percentage:\textit{89.2\%}}{SSMV Shahjahanpur}{Intermediate/+2 from CBSE}{2013--2015}{}{}

\cventry{CGPA:\textit{9.4/10}}{SSMV Shahjahanpur}{Matriculation from CBSE}{2011--2013}{}{}

\section{Experience}

\cventry{}{Manage database and server of online mess portal 'Rosei' of IIIT Bhubaneswar}{Web Administrator}{Sep 2017--present}{}{}

\section{Hackathons and Events}

\cventry{}{Google Developers Group Bhubaneswar}{\textbf{Devfest hackathon 2017}}{Sep 2017}{}{In this team based hackathon we were \textbf{Finalist}, in which we made a review analysis of products on e-commerce websites using Machine Learning.}

\cventry{}{Kronos India Pvt.Ltd. and Techgig.com}{\textbf{Kronothon 2017}}{Mar 2017}{}{\textbf{4th runner} up in the \textbf{pan India} Competitive coding contest}

\section{Projects}

\cventry{}{Live sentiment analysis of twitter}{Twitter Sentiment Analysis}{}{}{Tech Stack:Python Scikit-learn,nltk,matplotlib,tweepy}

\cventry{}{Automatic notice sender}{Hibiscut}{}{}{It automatically sends the official notices to the students via sms from the online notice board 'Hibiscus' of IIIT Bhubaneswar.
Tech Stack: Python Selenium, Requests,PhantomJS,urllib2}

\cventry{}{Tracks the employee in real time.}{Employee Tracking System}{}{}{Tech Stack:Javascript,php,Apache Cordova}

\section{Achivements and Honors}

\cvitem{Sep2017}{\textbf{Winner} of coding contest\textbf{'CodeNavratri'} organised by IIIT Bhubaneswar on hackerrank.}

\cvitem{Jan2017}{\textbf{2nd runner} in a team based competitive coding contest \textbf{'Swig'N'Code'} organised in tech fest 'Advaita' of IIIT Bhubaneswar.}

\cvitem{Dec2016}{\textbf{Winner} in Winter Development Challenge organised by Training and placement cell of IIIT Bhubaneswar.}

\cvitem{Nov2016}{\textbf{RunnerUp} in the competitive coding contest organised by ACM chapter of IIIT Bhubaneswar in 2016.}

\cvitem{Jan2015}{\textbf{Winner} in the mega coding contest TECHNOTHON organised by FIET,Bareilly.}

\section{Fields of Interest}
Machine Learning,Deep Learning,Natural Language Processing,Data Structures,Algorithms,Software Development

\section{Technical Skills}

\cvitem{Languages}{\ \ \textsc{python},\textsc{C},\textsc{C++}}
\cvitem{Frameworks}{\textsc{Keras},\textsc{Tensorflow}}
\cvitem{Tools}{\ \ \ \ \ \ \ \ \ \textsc{Git},\LaTeX,\textsc{Pycharm}}
\cvitem{Platforms}{\ \ \ \textsc{Linux},\textsc{Windows}}
\cvitem{Database}{\ \ \ \ \textsc{SQL}}

\section{Interests}
\renewcommand{\listitemsymbol}{-~}
\cvlistdoubleitem{Quora}{Football}
\cvlistdoubleitem{Cricket}{TableTennis}
\cvlistdoubleitem{Chess}{Music}
\end{document}






















